Joint Power Allocation and Network Slicing in an Open RAN System \vspace{-.1cm}

### 2020-05-12 Latex/tex/pr.tex
add paper

\textstyle \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{M_{s_1} + M_{s_2}}\bar{\Omega}_{\mathfrak{z},s}^f \;\; \mathfrak{z} \in \{M, S, C\}.

@@

@@

 &\textstyle  \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z},s}^f \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}  \forall s, \forall \mathfrak{z}\in \mathcal{E}; \label{c22}

@@

The optimization problem in \eqref{constraints} can be decomposed into two independent optimization problems A and B since the variables can be obtained independently and respectively. Firstly we need to solve problem A. After obtaining $\boldsymbol{P}$ and $ \boldsymbol{A}$, problem B can be solved by having the value of $ \boldsymbol{A}$. 
The problem A is as follow

@@

In problem B, $ \boldsymbol{Y}$ is obtained. The problem B is

@@

 &\textstyle  \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z},s}^f \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}
\forall s, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}

@@

In this subsection, a heuristic  method is proposed to solve the problem in \eqref{constraints1} which is non-convex and computationally hard. To make it tractable, we divide problem \eqref{constraints1} into

@@

In the first part of sub-problem A, we obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = P_{max}$ in \eqref{constraints1}. Also, we set $\eta = 0$. Afterward, by achieving $\boldsymbol{A}$, in the second part, we find $\boldsymbol{P}$ by using \eqref{constraints1}. This part of the problem can be approximated and converted to a convex problem, so the problem can be solved by convex methods. After solving $\boldsymbol{P}$, $\eta$ is updated. Then in the next iteration, with new $\boldsymbol{P}$
and $\eta$, the two parts of the problems are solved. We repeat this procedure until the algorithm  converges.
\subsection{First Part of Sub-Problem A}\label{firstsub}

@@

\subsection{Second Part of Sub-Problem A}\label{secondsub}

@@

\subsection{Solving two part of Sub-problem A iteratively}

@@

and $\eta$ the two parts of the problems is solved until the algorithm converges.
Here, the algorithm of solving sub-problem A is shown in algorithm \eqref{alg2}

@@

\subsection{Sub-Problem B}

>>>>

\textstyle \bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z},s}^f \;\; \mathfrak{z} \in \{M, S, C\}.

@@

Where, $F_s = M_{s_1} + M_{s_2}$

@@

 &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d, \forall \mathfrak{z}\in \mathcal{E}; \label{c22}

@@

The optimization problem in \eqref{constraints} can be decomposed into two independent optimization sub-problems 1 and 2 since the variables can be obtained independently and respectively. Firstly we need to solve sub-problem 1. After obtaining $\boldsymbol{P}$ and $ \boldsymbol{A}$, sub-problem 2 can be solved by having the value of $ \boldsymbol{A}$. 
The sub-problem 1 is as follow

@@

In sub-problem 2, $ \boldsymbol{Y}$ is obtained. The sub-problem 2 is

@@

 &\textstyle  \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}  \forall d,, \forall \mathfrak{z}\in \mathcal{E};  \label{eqomega}

@@

In this subsection, a heuristic  method is proposed to solve the problem in \eqref{constraints1} which is non-convex and computationally hard. To make it tractable, we divide the problem \eqref{constraints1} into

@@

In the first part of sub-problem 1, we obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = P_{max}$ in \eqref{constraints1}. Also, we set $\eta = 0$. Afterward, by achieving $\boldsymbol{A}$, in the second part, we find $\boldsymbol{P}$ by using \eqref{constraints1}. This part of the sub-problem can be approximated and converted to a convex problem, so the sub-problem can be solved by convex methods. After solving $\boldsymbol{P}$, $\eta$ is updated. Then in the next iteration, with new $\boldsymbol{P}$
and $\eta$, the two parts of the sub-problems are solved. We repeat this procedure until the algorithm  converges.
\subsection{First Part of Sub-Problem 1}\label{firstsub}

@@

\subsection{Second Part of Sub-Problem 1}\label{secondsub}

@@

\subsection{Solving two part of Sub-problem 1 iteratively}

@@

and $\eta$ the two parts of the sub-problem is solved until the algorithm converges.
Here, the algorithm of solving sub-problem 1 is shown in algorithm \eqref{alg2}

@@

\subsection{Sub-Problem 2}
